Hedonic House Prisce Model King County

### 2023-11-14 Msb205/Msb205kopi.Rmd
mmm

```{r Legge inn datasett. Dette fikk jeg ikke lastet ned som dbf-fil}
acs_b19101_familyincome <- read.csv("acs_b19101_familyincome.csv")
view(acs_b19101_familyincome)
```

@@

```{r}
library(readr)
acs_b02001_race <- read_csv("acs_b02001_race.csv")
#
#View(acs_b02001_race)
```

@@

```{r Laste ned kart}
file_path2 <- "Data/Kart/tracts10.shp"
tracts10 <- st_read(file_path2) #Les inn .shp-filen.
view(tracts10)
```

@@

## 3. Hus data

```{r}
library(dplyr)

# Convert the joining key in both dataframes to the same type if they are different
# For example, if GEO_ID_TRT is numeric in one and character in the other:
acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT)
acs_b19101_familyincome$GEO_ID_TRT <- as.character(acs_b19101_familyincome$GEO_ID_TRT)

@@

# Removing rows with missing values
husdata <- na.omit(joined_data)

# Viewing the data
View(husdata)

@@

```{r}
# Adjust the filtering criteria 'WADOH' county, useing COUNTY_STR
acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT) #til character
WADOH_KC_Etnisitet <- WADOH_King_County %>%
  left_join(acs_b02001_race, by = "GEO_ID_TRT")
```

@@

```{r}
# Renaming the Date column to year_month
WADOH_KC_Etnisitet <- WADOH_KC_Etnisitet %>%
  rename(year_month = date)
#view(WADOH_KC_Etnisitet)
```

>>>>

```{r Legge inn datasett. Dette fikk jeg ikke lastet ned som dbf-fil}
acs_b19101_familyincome <- read.csv("acs_b19101_familyincome.csv")
#view(acs_b19101_familyincome)
```

@@

```{r}
library(readr)
acs_b02001_race <- read_csv("acs_b02001_race.csv")

#View(acs_b02001_race)
```

@@

```{r Laste ned kart}
file_path2 <- "Data/Kart/tracts10.shp"
tracts10 <- st_read(file_path2) #Les inn .shp-filen.
#view(tracts10)
```

@@

## 3. Hus data = Inntekt og Etnisitet

```{r}
# Convert the joining key in both dataframes to the same type if they are different
# For example, if GEO_ID_TRT is numeric in one and character in the other:

acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT)
acs_b19101_familyincome$GEO_ID_TRT <- as.character(acs_b19101_familyincome$GEO_ID_TRT)

@@

#Removing rows with missing values
husdata <- na.omit(joined_data)

View(husdata)

@@

```{r}
# Adjust the filtering criteria 'WADOH' county, useing COUNTY_STR
acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT) #til character
WADOH_KC_Etnisitet <- WADOH_King_County %>%
  left_join(acs_b02001_race, by = "GEO_ID_TRT")
view(WADOH_KC_Etnisitet)
```

@@

```{r}
# Renaming the Date column to year_month
WADOH_KC_Etnisitet <- WADOH_KC_Etnisitet %>%
  rename(year_month = date)
view(WADOH_KC_Etnisitet)
```
